---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning=FALSE, 
  message=FALSE
)
```
# gpt2samples

The goal of gpt2samples is to help users explore the various sample texts as generated by Open AI's new GPT2 transformer based language model. 

An original implementation of a smaller version of GPT-2 can be found [here](https://github.com/openai/gpt-2), and the original sample text files can be found [here](https://github.com/openai/gpt-2/tree/master/gpt-2-samples).

## Data

This package contains the following data, stored as tibbles:

|tibble                 |description                                                                                                                           |
|:--------------------|:-------------------------------------------------------------------------------------------------------------------------------------|
|conditional-t07      |Conditionally generated samples, with context prompts from `WebText` test corpus, default settings (temperature 1 and no truncation). |
|conditional-topk40   |Conditionally generated samples, with context prompts from `WebText` test corpus, with temperature 0.7                                |
|conditional          |Conditionally generated samples, with context prompts from `WebText` test corpus, with truncation and top_k 40.                       |
|unconditional        |Unconditionally generated samples, default settings.                                                                                  |
|unconditional-t07    |Unconditionally generated samples, with temperature 0.7                                                                               |
|unconditional-topk40 |Unconditionally generated samples, with truncation and top_k 40.

Additionally, all the generated samples (conditional and unconditional) can be explored by calling `all_samples()`. 

## Installation

<!-- You can install the released version of gpt2samples from [CRAN](https://CRAN.R-project.org) with:-->

You can install the released version of gpt2samples from GitHub with:

```r
# install.packages("gpt2samples")
# install.packages("devtools")
devtools::install_github("kanishkamisra/gpt2samples")
```

## Example

This is a basic example to explore the data using dplyr verbs

```{r example}
library(dplyr)
library(gpt2samples)

conditional %>%
  filter(id == 100)

unconditional_t07 %>%
  filter(id == 250)

all_samples() %>%
  group_by(file) %>%
  summarise(total_lines = n())
```


Additional exploration can use Julia Silge and David Robinson's `tidytext` [package](https://cran.r-project.org/web/packages/tidytext/index.html), among others to analyze the generated text as produced by GPT-2.

## Contributor Code of Conduct
Please note that the 'gpt2samples' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
