---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning=FALSE, 
  message=FALSE
)
```
# gpt2samples

The goal of gpt2samples is to help users explore the various sample texts as generated by Open AI's language model.

An original implementation of a smaller version of GPT-2 can be found [here](https://github.com/openai/gpt-2).

## Data

This package contains the following data, stored as tibbles:

## Installation

<!-- You can install the released version of gpt2samples from [CRAN](https://CRAN.R-project.org) with:-->

You can install the released version of gpt2samples from GitHub with:

```r
# install.packages("gpt2samples")
# install.packages("devtools")
devtools::install_github("kanishkamisra/gpt2samples")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
library(dplyr)
library(gpt2samples)

conditional %>%
  filter(id == 100)
```


## Contributor Code of Conduct
Please note that the 'gpt2samples' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
